\begin{thebibliography}{30}
	\bibitem{L. Euler}
	L. Euler, \textit{De serie Lambertina plurimisque eius insignibus proprietatibus}, Leonhardi Euleri Opera Omnia, Ser. 1, Opera Mathematica, $\pmb{6}$, 1921 (orig. date 1779), 350-369. 
	\bibitem{S. Janson}
	S. Janson, D.E.Knuth, T.Luczak, and B.Pittel, \textit{The birth of the giant component, Random Structures and Algorithms}, $\pmb{4}$ (1993) 233-358.
	\bibitem{C.W. Borchardt}
	C.W.Borchardt, \textit{Ueber eine der Interpolation entsprechende Darstellung der Eliminations-Resultante}, J.reine angewandte Math. $\pmb{57}$ (1860) 111-121.
	\bibitem{Cayley}
	A. Cayley, \textit{A theorem of trees}, Quarterly Journal of Mathematics, Oxford Series, $\pmb{23}$ (1889) 376-378.
	\bibitem{Skovgaard}
	O. Skovgaard, I.G. Jonsson, and J.A.Bertelsen, \textit{Computation of wave heights due to refraction and friction}, J. Waterways Harbours and Coastal Engineering Division, February, 1975, pp 15-32.
	\bibitem{Polya}
	G. Polya and G. Szego, \textit{Problems and Theorems in Analysis}, Springer-Verlag, 1972.
	\bibitem{Corless}
	R.M. Corless and D.J. Jeffrey, \textit{Well, It Isn't Quite That Simple}, SIGSAM Bulletin, $\pmb{26}$, 3 (1992) 2-6.
	\bibitem{Graham}
	R.L. Graham, D.E. Knuth, O. Patashnik, \textit{Concrete Mathematics}, Addison-Wesley, 1994.
	\bibitem{Jeffrey}
	D.J. Jeffrey, R.M. Corless, D.E.G. Hare, \textit{Unwinding the banches of the Lambert W function}, The Mathematical Scientist, in press.
	\bibitem{Ranger}
	K.B. Ranger, \textit{A complex variable integration technique for the 2-dimensional Navier-Stockes equations}, Q. Applied Maths, $\pmb{49}$ (1991) 555-562.
	\bibitem{Parker}
	F.D. Parker, \textit{Integrals of inverse functions}, Amer. Math. Monthly, $\pmb{62}$, (1955), 439-440.
	\bibitem{Geddes}
	K.O. Geddes, S.R. Czapor and G.Labahn, \textit{Algorithms for Computer Algebra}, Kluwer Academic Publisher, 1992.
	\bibitem{Malley}
	R.E. O'Malley, Jr., \textit{Singular Perturbation Methods for Ordinary Differential Equations}, Springer-Verlag Applied Mathematical Sciences, $\pmb{89}$, 1991.
	\bibitem{Reiss}
	E.L. Reiss, \textit{A new asymptotic method for jump phenomena}, SIAM J.Appl. Math. $\pmb{39}$ (1980) 440-455.
	\bibitem{Bellman}
	R.E. Bellman and K.L. Cooke, \textit{Differential-Difference Equations}, Academic Press, 1963.
	\bibitem{Corless}
	R.E. Corless, \textit{Essential Maple}, Spring-Verlag 1994.
	\bibitem{Wright}
	E.M. Wright, \textit{The linear difference-differential equation with constant coeffcients}, Proc. Royal Soc. Edinburgh, A$\pmb{62}$ (1949) 387-393.
	\bibitem{Hale}
	J. K. Hale and S. M. V. Lunel., \textit{Introduction to Functional Differential Equations}, volume 99 of \textit{Applied mathematical sciences.} Springer-Verlag, 1993.
	\bibitem{Corless}
	R. Corless, G.H. Gonnet, D.E.G. Hare, D.J. Jeffrey, and D.E. Knuth, \textit{On the Lambert W function}. Adv. Comput. Math., 5:329-359, 1996.
	\bibitem{Asl}
	F. M. Asl and A. G. Ulsoy, \textit{Analysis of a system of linear delay differential equations}. J. Dyn. Syst. Meas. Control, 125:215-223, 2003.
	\bibitem{Yi}
	S. Yi and A. G. Ulsoy, \textit{Solution of a system of linear delay differential equations using the matrix Lambert function.} In Proc. 26th American Control Conference, Minneapolis, pages 2433-2438, 2006.
	\bibitem{Yi}
	S. Yi, A. G. Ulsoy, and P. W. Nelson, \textit{Solution of a system of linear delay differential equations using the matrix Lambert function and the Laplace transformation. Automatica,} 2006.
	\bibitem{Shinozaki}
	H. Shinozaki and T. Mori. Robust stability analysis of linear time-delay systems by Lambert W function: Some extreme point results, \textit{Automatica}, 42(10):1791-1799, 2006.
	\bibitem{Horn}
	R. Horn and C.R. Johnson, \textit{Topics in Matrix Analysis}. Cambridge University Press, Cambridge, UK, 1991.
	\bibitem{Higham}
	N. Higham. Functions of matrices. In L. Hogben, editor, \textit{Handbook of Linear Algebra}. CRC Press, 2006.
	\bibitem{Radjavi}
	H. Radjavi and P. Rosenthal, \textit{Simultaneuos Triangularization}. Springer-Verlag, New York, 2000.
	\bibitem{Sontag}
	E. D. Sontag, \textit{Mathematical Control Theory, Determineistic Finite Dimensional Systems}. Springer-Verlag, New York, 2nd edition, 1998. 
	\bibitem{On}
	\textit{On the Lambert W function}, R.M. Corless, D.E.G. Hare, D.J. Jeffrey, and D.E.Knuth 
	\bibitem{Spectrum}
	\textit{The Lambert W function and the spectrum of some multidimensional time-delay systems}, Elias Jarlebring, Tobias Damm. 
	\bibitem{dimensitional}
	\textit{Some special cases in the stability analysis of multi-dimensional time-delay systems using the matrix Lambert W function}, Rudy Cepeda-Gomez, Wim Michiels.
\end{thebibliography}
Bài tiểu luận được tham khảo từ 3 nguồn tham khảo chính $[28,29,30]$
