\begin{thebibliography}{99} % Tài liệu tham khảo
	\addcontentsline{toc}{chapter}{{\bf Tài liệu tham khảo}\rm}

\bibitem{Br98} 
Branicky, M.S., Multiple Lyapunov functions and other analysis tools for switched and hybrid systems, \emph{IEEE Transactions on Automatic Control}, 1998. 

\bibitem{LTW11} 
Daniel Liberzon, Stephan Trenn and Fabian Wirth, Commutativity and asymptotic stability for linear switched DAEs. \emph{2011 50th IEEE Conference on Decision and Control and European Control Conference (CDC-ECC) Orlando, FL, USA}, December 12-15, 2011.

\bibitem{Masu97} I. Masubuchi, Y. Kamitane, A. Ohara, and N. Suda, $\mathcal{H}_{\infty}$ control for descriptor systems: a matix inequalities approach  \emph{Automatica}, 1997.

\bibitem{Nar94} Narendra, K.S and Balakrishnan,J.. A common Lyapunov function for stable LTI systems with commuting A-matrices, \emph{IEEE Transactions on Automatic Control}, 1994.

\bibitem{E99} E. Uezato and M. Ikeda, Strict LMI conditions for stability, robust stabilization, and $\mathcal{H}_{\infty}$ control of descriptor systems, \emph{Proc. of the 38th IEEE Conference on Decision and Control}, Phoenix, USA 1999.

\bibitem{M98} M. A. Wicks, P. Peleties, and R. A. DeCarlo, Swithched controller design for the quadratic stabilization of a pair of unstable linear systems  \emph{European Journal of Control}, 1998.

\bibitem{Xu99} Xu, S. and Yang, C. .Stabilization of discrete-time singular systems: A matrix inequalities opproach, \emph{Automatica}, 1999.

\bibitem{Zhai09a} 
Guisheng Zhai, Ryuuen Kou, Joe Imae, and Tomoaki Kobayashi,	Stability Analysis and Design for Switched Descriptor Systems,  \emph{International Journal of Control, Automation, and Systems} (2009) 7(3):349-355.

\bibitem{Zhai10} Guisheng Zhai, Xuping Xu, A unified approach to stability analysis of switched linear descriptor symtems under arbitrary switching,	\emph{International Journal of Applied Mathematics and Computer Science}, 2010, Vol. 20, No. 2, 249–259.

\bibitem{book1} Dan Zhang, Li Yu, {\itshape Analysis and Synthesis of Switched Time-Delay Systems: The Average Dwell Time Approach}, Springer, 2019.


% 	\bibitem {1} \label{tltk1}
% 	W. Chen, C. Li, Y. Li; {\itshape A direct method of moving planes for the fractional Laplacian} , Adv. Math. 308 (2017) 404–437.
	
% 	\bibitem {2} \label{tltk2}
% 	W. Chen, C. Li, B. Ou; {\itshape Classification of solutions for an integral equation} , Comm. Pure Appl. Math. 59 (2006) 330–343.
	
% 	\bibitem {3} \label{tltk3}
% 	W. Dai, Y. Fang, J. Huang, Y. Qin, B. Wang; {\itshape Regularity and classification of solutions to static Hartree equations involving fractional Laplacians} , Discrete Contin. Dyn. Syst. Ser. A 38 (2018) 2795–2809.
	
% 	\bibitem {4} \label{tltk4}
% 	T. Kulczycki; {\itshape Properties of green function of symmetric stable processes} , Probab. Math. Stat. 17 (1997) 339–364.
	
% 	\bibitem {5} \label{tltk5}
% 	E. Lieb; {\itshape Sharp constants in the Hardy-Littlewood-Sobolev and related inequalities} , Ann. of Math. 118 (1983) 349–374.
	
% 	\bibitem {6} \label{tltk6}
% 	B. Ou; {\itshape A remark on a singular integral equation} , Houston J. Math. 25 (1999) 181–184.
	
% 	\bibitem {7} \label{tltk7}
% 	Phuong Le; {\itshape Liouville theorem and classification of positive solutions for a fractional Choquard type equation}, Nonlinear Anal. 185 (2019) 123-141.
	
% 	\bibitem {8} \label{tltk8}
% 	L. Silvestre; {\itshape Regularity of the obstacle problem for a fractional power of the Laplace operator} , Comm. Pure Appl. Math.
% 	60 (2007) 67–112.
	
	
% 	\bibitem {9} \label{tltk9}
% 	R. Zhuo, W. Chen, X. Cui, Z. Yuan; {\itshape A Liouville theorem for the fractional Laplacian}, preprint, arXiv:1401.7402.
\end{thebibliography}
